Paper Title*\\

### 2019-05-09 latex-template/paper.tex
update testing results

\section{Testing}
\section{Limitations and Challenges}
\section{Related Works}
Not a lot of work have been done regarding this specific problem. Following few pieces of work have some indirect relations with our work. 
\begin{itemize}
	\item {\textbf{Classification of Callbacks:}
		This paper does in depth analysis of 138 JavaScript pages with over 5 million 
		lines of codes. Study shows that around every 10th function takes a callback as an argument and 43\% of these callbacks are anonymous functions. Among these functions almost half are asynchronous calls. This shows importance of a tool that polices callbacks to ensure callbacks do not become too complicated \cite{b3}. 
	}
	\item{\textbf{Synchronous to Asynchronous:}
		Realizing the importance and usefulness of asynchronous programming, this work introduces way to convert to synchronous code of JavaScript to asynchronous to improve responsiveness of mobile apps \cite{b1}. 
	}
	\item{\textbf{Detecting JS code smells:}
		This paper does analysis of a sample of JavaScript programs and finds most common coding flaws. It presents a way of detecting these code smells. A notable code smell it talks about is nested callbacks, which can become hard to read and consequently debug. However, it only detects these code smells and does not provide any solution. Our work extends on this explicit problem and we try to cover a subset of problems caused by callbacks and try to solve \cite{b2}. 
	}
\end{itemize}
\section{Conclusion}
Callbacks can ensure very smooth and prompt execution of program if they are implemented rightly. However, since callbacks tend to get complex as they get nested they might even affect asynchrony of program execution. Our approach tends to find such abnormalities in JavaScript programs and improves performance by refactoring such instructions to position where they are executed earlier without affecting functionality of program. We achieve this goal by extracting AST of code using a JavaScript library UglifyJS, next we extract execution context from the AST and finally based on this AST and few rules we choose which instructions can be refactored. These instructions are removed from current function’s body and are placed in callee function’s body. Our approach currently only works on JavaScript ECMAscript 5 due to compatibility issues of UglifyJS, but it can be extended to newer versions if replacement for UglifyJS is found.

>>>>

\section{Testing}
We tested our results on multiple JavaScript files from some npm modules as well as a few self-written files. Due to certain limitations we got a large number of false positives, however, we figured that by handling more cases we could get rid of these false positives. On a total of 9 JavaScript files with a total 2239 lines of code, our implementation of proposed technique suggested a total of 1472 instructions that could be refactored. This should be noted that an instruction can be counted towards being refactored more than once when it is nested into callbacks multiple times. In fact, the JavaScript files we explicitly took up for testing were those which had a large number of nested callbacks with a significant number of these callbacks being anonymous functions. We picked files of multiple lengths varying from tens of lines of code to about 1000 lines of code. Maximum number of refactoring suggestion we got were 850 for a file with 980 lines of code. Most common types of false positives were:  function call with a value instead of placeholder variable, duplicate names in nested callbacks and some instructions that user expects execute at certain place for example socket.close() or console,log(). Although,a very significant proportion of suggestions we got from our implementation were false positives, we expect results to improve reasonably once more corner cases are catered.

\section{Limitations and Challenges}
\section{Related Works}
Not a lot of work have been done regarding this specific problem. Following few pieces of work have some indirect relations with our work. 
\begin{itemize}
	\item {\textbf{Classification of Callbacks:}
		This paper does in depth analysis of 138 JavaScript pages with over 5 million 
		lines of codes. Study shows that around every 10th function takes a callback as an argument and 43\% of these callbacks are anonymous functions. Among these functions almost half are asynchronous calls. This shows importance of a tool that polices callbacks to ensure callbacks do not become too complicated \cite{b3}. 
	}
	\item{\textbf{Synchronous to Asynchronous:}
		Realizing the importance and usefulness of asynchronous programming, this work introduces way to convert to synchronous code of JavaScript to asynchronous to improve responsiveness of mobile apps \cite{b1}. 
	}
	\item{\textbf{Detecting JS code smells:}
		This paper does analysis of a sample of JavaScript programs and finds most common coding flaws. It presents a way of detecting these code smells. A notable code smell it talks about is nested callbacks, which can become hard to read and consequently debug. However, it only detects these code smells and does not provide any solution. Our work extends on this explicit problem and we try to cover a subset of problems caused by callbacks and try to solve \cite{b2}. 
	}
\end{itemize}
\section{Conclusion}
Callbacks can ensure very smooth and prompt execution of program if they are implemented rightly. However, since callbacks tend to get complex as they get nested they might even affect asynchrony of program execution. Our approach tends to find such abnormalities in JavaScript programs and improves performance by refactoring such instructions to position where they are executed earlier without affecting functionality of program. We achieve this goal by extracting AST of code using a JavaScript library UglifyJS, next we extract execution context from the AST and finally based on this AST and few rules we choose which instructions can be refactored. These instructions are removed from current function’s body and are placed in callee function’s body. Our approach currently only works on JavaScript ECMAscript 5 due to compatibility issues of UglifyJS, but it can be extended to newer versions if replacement for UglifyJS is found.
